\bibitem{benchmarkfood}
X. Wu, X. Fu, Y. Liu, E.-P. Lim, S. C. H. Hoi, and Q. Sun, ``A large-scale benchmark for food image segmentation,'' 2021, arXiv:2105.05409. [Online]. Available: https://arxiv.org/abs/2105.05409

% \bibitem{godfray2010foodsecurity}
% H. C. J. Godfray et al., ``Food security: The challenge of feeding 9 billion people,'' \textit{Science}, vol. 327, no. 5967, pp. 812--818, 2010.

% \bibitem{alexandratos1995world}
% N. Alexandratos, Ed., \textit{World Agriculture: Towards 2010: An FAO Study}. Food \& Agriculture Organization, 1995.

\bibitem{mahalik2010trends}
N. P. Mahalik and A. N. Nambiar, ``Trends in food packaging and manufacturing systems and technology,'' \textit{Trends in Food Science \& Technology}, vol. 21, no. 3, pp. 117--128, 2010.

\bibitem{stemmer2018vision}
Stemmer Imaging, ``Vision technology for the food and beverage industry,'' Stemmer Imaging Market Brochure, 2018.

\bibitem{gao2019smartfridge}
X. Gao et al., ``Research on food recognition of smart refrigerator based on SSD target detection algorithm,'' in \textit{Proc. Int. Conf. Artificial Intelligence and Computer Science}, 2019, pp. 303--308.

\bibitem{wang2019smartrefrigerator}
K. Wang et al., ``A smart refrigerator architecture that reduces food ingredients waste materials and energy consumption,'' \textit{Ekoloji Dergisi}, no. 107, 2019.

\bibitem{zhuang2020transfer}
F. Zhuang et al., ``A comprehensive survey on transfer learning,'' \textit{Proc. IEEE}, vol. 109, no. 1, pp. 43--76, 2021.

\bibitem{he2015residual}
K. He, X. Zhang, S. Ren, and J. Sun, ``Deep residual learning for image recognition,'' \textit{arXiv preprint arXiv:1512.03385}, 2015.

\bibitem{dong2020mobilenetv2}
K. Dong, C. Zhou, Y. Ruan, and Y. Li, ``MobileNetV2 model for image classification,'' in \textit{Proc. 2nd Int. Conf. Information Technology and Computer Application (ITCA)}, 2020, pp. 476--480.

% \bibitem{yanai2015foodimage}
% K. Yanai and Y. Kawano, ``Food image recognition using deep convolutional network with pre-training and fine-tuning,'' in \textit{Proc. IEEE Int. Conf. Multimedia \& Expo Workshops (ICMEW)}, 2015, pp. 1--6.

% \bibitem{lubura2022foodrecognition}
% J. Lubura et al., ``Food recognition and food waste estimation using convolutional neural network,'' \textit{Electronics}, vol. 11, no. 22, p. 3746, 2022.

% \bibitem{chakraborty2024aikitchen}
% S. Chakraborty and S. Aithal, ``AI kitchen,'' \textit{Int. J. Applied Engineering and Management Letters}, vol. 8, pp. 128--137, 2024.
